Fast Radio Burst Cosmology

### 2014-04-10 writeup/dm_angular_ps.tex
Sketched out how to get to teh estimator.

@@

We further assume that $\{D^{\rm src}_i\}$ are uncorrelated. Again this may not
be strictly true due to clustering of FRB sources and again this may bias our
estimator. We parameterized the variance from this term as 
\begin{equation}
    \langle D^{\rm src}_i D^{\rm src}_j \rangle
    - \langle D^{\rm src}_i \rangle \langle D^{\rm src}_j \rangle
    = \delta_{ij} \sigma^2_{\rm src}
\end{equation}

We further assume that the terms in Equation \ref{e:D_sep} are mutually uncorrelated

>>>>

\newcommand{\ud}{\,\mathrm{d}}

@@

We further assume that $\{D^{\rm src}_i\}$ are uncorrelated. Again this may not
be strictly true due to clustering of FRB sources and again this may bias our
estimator. We parameterized the variance from this term as 
\begin{equation}
    \langle D^{\rm src}_i D^{\rm src}_j \rangle
    - \langle D^{\rm src}_i \rangle \langle D^{\rm src}_j \rangle
    = \delta_{ij} \sigma^2_{\rm src}.
\end{equation}

The cosmological information lies in the correlations within the set
$\{D^{\delta_e}_i\}$. If the redshifts of the observed FRBs where known, we
would write the probability density function of this set as
$p(\{D^{\delta_e}_i\} | \{z_i\})$, which has second moments
\begin{equation}
    w^{z_i z_j}(\hat{n}_i\cdot\hat{n}_j) \equiv \int \ud \{D^{\delta_e}_i\}
        D^{\delta_e}_i D^{\delta_e}_j p(\{D^{\delta_e}_i\} | \{z_i\}).
\end{equation}
$w^{z_i z_j}(\hat{n}_i\cdot\hat{n}_j)$ is the redshift dependant DM angular
correlation function, whose dependence on cosmology is derived below.
Marginalizing $p(\{D^{\delta_e}_i\} | \{z_i\})$ over the unknown redshifts
yields
\begin{equation}
    p(\{D^{\delta_e}_i\}) = \int_0^\infty \ud \{z_i\}
        p(\{z_i\}) p(\{D^{\delta_e}_i\} | \{z_i\}).
\end{equation}
The second moment of the marginalized distribution is
\begin{align}
    \langle D^{\delta_e}_i D^{\delta_e}_j \rangle =& \\
        =& \textrm{stuff} \\
    =& \int \ud z \ud z' p(z) p(z') w^{z z'}(\hat{n}_i\cdot\hat{n}_j) \qquad (i \neq j) \\
    =& \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(\hat{n}_i\cdot\hat{n}_j)
    \qquad (i = j)
\end{align}
I think.

The covariance matrix is
\begin{align}
    C_{ij} =& \langle D_i D_j \rangle - \langle D_i \rangle \langle D_j \rangle
           = \textrm{a bunch of things we know (special case for $i=j$)}.
\end{align}

Now that we have the covariance matrix, the estimator is Equation~11.94 from
Dodelson, although we have to modify it slightly to exclude the
auto-correlations.  The error (assuming Gaussianity) is Equation~11.100.

%We further assume that the terms in Equation \ref{e:D_sep} are mutually uncorrelated
